Primate Cognition and the Red Queen Hypothesis

### 2021-05-11 Article/Article.Rmd
Correct typos in script/redaction

output: 
 #      - '--lua-filter=scholarly-metadata.lua'
 #      - '--lua-filter=author-info-blocks.lua'
 bookdown::pdf_book:
 #bookdown::word_document2:
   number_sections: false
   toc: false
   #citation_package: natbib
   latex_engine: pdflatex
   fig_caption: true
   pandoc_args:
     - '--lua-filter=scholarly-metadata.lua'
     - '--lua-filter=author-info-blocks.lua'

@@

#Load environments
load("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Data_spatial_primate.RData")
load("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/geography_traits_biogeobears.RData")

>>>>

output: 
 #      - '--lua-filter=scholarly-metadata.lua'
 #      - '--lua-filter=author-info-blocks.lua'
 #bookdown::pdf_book:
 bookdown::word_document2:
   number_sections: false
   toc: false
   #citation_package: natbib
   latex_engine: pdflatex
   fig_caption: true
   pandoc_args:
     - '--lua-filter=scholarly-metadata.lua'
     - '--lua-filter=author-info-blocks.lua'

@@

#Load environments
load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsData_spatial_primate.RData")
load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsgeography_traits_biogeobears.RData")
